Stat 400 Presentation

### 2021-12-08 Stat 400 presentation.Rmd
finished intro slides + image

##

@@

- Step Function
    - Consider dots on a plane, with random

- This is approached through an SIR model: Susceptible, Infected, Recovered. All change based on time.

@@

- not complete

>>>>

@@

- Step Function
  ![Sample](/cloud/project/image.jpg)

- This is approached through an SIR model: Susceptible, Infected, Recovered. All change based on time as the function iterates through a set number of days. 
  - 0.5% of the initial subjects start out with the virus (infected)
  - 99.5% subjects are susceptible
  - 0% recovered

@@

- Factors to consider in the transmission of a virus. 
  - What is the relationship and distribution between the infection probability and the physical distance
  - High/low virus load, varying physical distances, ineffective vs effective mask wearing. 
  - Environmental conditions: humidity, temperature, air ventilation. 
- Based on real epidemiological data analysis, these encompassing factors will be distributed Exponential(rate = lambda)
- Recovery and Incubation times ~ Gamma(alpha, beta), But in order to get whole number for days, we distribute them Possion(lambda)
